Essays in Computational Management Science

### 2018-05-11 Chapters/Chapter02.tex
sdm done.

from call admission control \citep{kwon_atm_1998, hee-yong_kwon_atm_1997}, to behavior-based robotics \citep{Rajesh1998, mendes2008robot, jockel_sparse_2009}, to noise filtering \citep{meng_modified_2009} and many others

There has recently been a surge of hardware implementations to minimize energy expenditure \citep{kang_energy-efficient_2015, kang_-memory_2016, li_hyperdimensional_2016, montagna_pulp-hd:_2018, salahuddin_energy_nodate}.

see the recent work on modern machine learning and reinforcement learning \citep{aguiar_sdm-go:_2013, wu_kanerva_2018}

@@

Our motivation is our own effort to run our models. As there is no reference implementation, we had to develop our own and run several simulations to ensure that our implementation was correct and bug-free. Thus, we had to deviate from our primary goal --- which was to test our hypothesis and explore the `ideas space' --- and to focus on the implementation itself. Furthermore, new members of our research group had to go through different source code developed by former members, in different languages.  Consider the implementations of SDM present --- as of this writing --- on its wikipedia entry\citep{noauthor_sparse_2018}:

>>>>

@@

Our motivation is our own effort to run our models. As there is no reference implementation, we had to develop our own and run several simulations to ensure that our implementation was correct and bug-free. Thus, we had to deviate from our primary goal --- which was to test our hypothesis and explore the `ideas space' --- and to focus on the implementation itself. Furthermore, new members of our research group had to go through different source code developed by former members, in different languages.  Consider the implementations of SDM present --- as of this writing --- on its wikipedia entry\citep{noauthor_sparse_2018}\footnote{There has recently been a surge of hardware implementations to minimize energy expenditure and parallelize processes \citep{kang_energy-efficient_2015, kang_-memory_2016, li_hyperdimensional_2016, montagna_pulp-hd:_2018, salahuddin_energy_nodate}.  While these implementations are extremely interesting, they do not afford the flexibility to experiment that software does.}:
